---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# listdown

<!-- badges: start -->
[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
[![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)
<!-- badges: end -->

## Overview 

The listdown package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. From the list, 
listdown creates a workflowr, pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document  with all tables and visualization that will appear. This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions.

listdown provides a reproducible means for _analytical_ document elements. It is most compatible with
data analysis pipelines where the data format is fixed but the analyses are either being updated, 
which may affect _narrative_ elements including the result discussion and conclusion, or where the
experiment is different, which affects all narrative elements.

## Installation

<!--
You can install the released version of listdown from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("listdown")
```

And the development version from [GitHub](https://github.com/) with:
-->

You can install the development version of listdown from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kaneplusplus/listdown")
```

<!-- 
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(listdown)
## basic example code
```
-->
